Complementary roles of Theta and Alpha in Multi-Item Associations

### 2020-01-14 supplemental.tex
tims feedback on response

\subsection{High vs. Low Confidence EEG Clusters}
\label{sec:deevEEGConf}
Here trials were selected based on the confidence ratings given for each retrieval attempt with the intention of capturing differences in EEG time frequency for Recollection vs. Familiarity based memory retrieval.  The same analysis approach used in the closed-loop vs. open-loop results was adopted for this confidence contrast (i.e. cluster based search in Stimulus Locked and Response Locked within theta, alpha and beta frequency bands).  All correctly retrieved trials with confidence rating less then 3 were assigned to the Low Confidence condition, and all correctly retrieved trials with confidence greater then 2 were assigned to the High Confidence condition (trial counts: low confidence correct $\mu=25\pm4$ 95\% confidence interval across subjects, high confidence correct $\mu=127\pm33$).  It should be noted that this difference in trial counts per condition should not impact the type 1 error rate of the cluster statistics as significance is calculated through a bootstrapped random permutation of condition labels across subjects.

@@

\begin{figure}
  \centering\includegraphics[width=1\textwidth]{figs/fig_deepleabra_attn_compute_edit.pdf}
  \caption[Signal Flow Through Cortical Layers in Deep LEABRA]{\small How attentional modulation is computed in response to a top-down attentional focus.  \emph{(A)} Layer 4 receives bottom-up sensory input, which then drives superficial layers (2/3), which initially do not reflect the attentional modulation (not shown).  The deep layer 5 Intrinsic Bursting (5IB) neurons integrate deep-to-deep top-down attentional inputs plus the local stimulus features from 2/3, to produce a {\em raw} deep output, prior to the contextual normalization process.  Layer 6 Cortical-Thalamic (6CT) neurons then integrate this direct activation from 5IB, to produce, for the first time in the circuit, a properly renormalized multiplicative gain-field activation pattern, with surround inhibition both within the 6CT layer and further downstream in the  TRC circuit providing the renormalization process.  These 6CT activations then modulate (multiply) the superficial-layer activations to produce {\em both} an increase in the attended location, and a decrease for the unattended location, as shown.  
\emph{(B)} Implementation of computational principle within the Theta-Phase network.  In the model layer 4 is subsumed into layer 2/3 neurons, as represented by ECin and ECout.  Top down influence comes from the hippocampus via area CA1 connections to ECout.  Layer 5IB \emph{raw} signals are calculated from ECin and ECout, and in turn used to calculate the \emph{mod} signal.  This layer 6CT project to the TRC units which ultimately are used to modulate the EC superficial layers with the current attentional mask. 
  }
  \label{fig:attn_compute}
\end{figure}

>>>>

\subsection{High vs. Low Confidence EEG Clusters}
\label{sec:deevEEGConf}
Here trials were selected based on the confidence ratings given for each retrieval attempt with the intention of capturing differences in EEG time frequency for Recollection vs. Familiarity based memory retrieval.  The same analysis approach used in the closed-loop vs. open-loop results was adopted for this confidence contrast (i.e. cluster based search in Stimulus Locked and Response Locked within theta, alpha and beta frequency bands).  Confidence ratings were a 4 point scale with 1 being high confidence and 4 being low confidence. All correctly retrieved trials with confidence rating less then 3 were assigned to the Low Confidence condition, and all correctly retrieved trials with confidence greater then 2 were assigned to the High Confidence condition (trial counts: low confidence correct $\mu=25\pm4$ 95\% confidence interval across subjects, high confidence correct $\mu=127\pm33$).  It should be noted that this difference in trial counts per condition should not impact the type 1 error rate of the cluster statistics as significance is calculated through a bootstrapped random permutation of condition labels across subjects.

@@

\begin{figure}
  \centering\includegraphics[width=1\textwidth]{figs/fig_deepleabra_attn_compute_edit.pdf}
  \caption[Signal Flow Through Cortical Layers in Deep LEABRA]{\small How attentional modulation is computed in response to a top-down attentional focus.  \emph{(A)} Layer 4 receives bottom-up sensory input, which then drives superficial layers (2/3), which initially do not reflect the attentional modulation (not shown).  The deep layer 5 Intrinsic Bursting (5IB) neurons integrate deep-to-deep top-down attentional inputs plus the local stimulus features from 2/3, to produce a {\em raw} deep output, prior to the contextual normalization process.  Layer 6 Cortical-Thalamic (6CT) neurons then integrate this direct activation from 5IB, to produce, for the first time in the circuit, a properly renormalized multiplicative gain-field activation pattern, with surround inhibition both within the 6CT layer and further downstream in the  TRC circuit providing the renormalization process.  These 6CT activations then modulate (multiply) the superficial-layer activations to produce {\em both} an increase in the attended location, and a decrease for the unattended location, as shown.  
\emph{(B)} Implementation of computational principle within the attention augmented Theta-Phase network.  In the model layer 4 is subsumed into layer 2/3 neurons, as represented by ECin and ECout.  Top down influence comes from the hippocampus via area CA1 connections to ECout.  Layer 5IB \emph{raw} signals are calculated from ECin and ECout, and in turn used to calculate the \emph{mod} signal.  This layer 6CT projects to the TRC units which ultimately are used to modulate the EC superficial layers with the current attentional mask. 
  }
  \label{fig:attn_compute}
\end{figure}
